\documentclass[a4paper]{article}

% Import some useful packages
\usepackage[margin=0.5in]{geometry} % narrow margins
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.95}

\title{Peer-review of assignment 4 for \textit{INF3331-dawoodah }}
\author{Reviewer 1, sebastgj, {seb.gjertsen@gmail.com} \\
 		Reviewer 2, ferdinae, {ferdinae@ulrik.uio.no} \\
		Reviewer 3, nithusht, {nithusht@ulrik.uio.no}}

\begin{document}
\maketitle

\section{Review} \label{sec:review}

Linux with Python 3.5 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{General feedback}
Could improve the structure of the code and use function.
Zero docstrings implemented.
Numbers in the mandelbrotset should be black. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.1: Python implementation}
Satisfactory solution. Set lower default values to lower first runtime. Reviewers were very impatient. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.2:  numpy implementation} \label{sec:assignment5.2}

\begin{itemize}
  \item Satisfactory code. 
  \item Nice runtime 
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.3: Integrated C implementation}
\begin{itemize}
  \item Just about satisfactory
  \item Loops not fully optimized
  \item Could have used more Cython code 
  \item Cpdef instead of def calculate()
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.4:  An alternative integrated C implementation}
Not implemented

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.5: User interface}
\begin{itemize}
\item Just about acceptable.
\item Not user friendly enough.  
\item Does not take filename as argument, hence not saving to file. 
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.6:  Packaging and unit tests}
Not implemented 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 4.7: More color scales + art contest}
\begin{itemize}
\item Acceptable
\item Could be wrapped in earlier functions, not run as command
\end{itemize}
\subsection*{Assignment 4.8: Self replication}
Acceptable

\bibliographystyle{plain}
\bibliography{literature}

\end{document}