\documentclass[a4paper]{article}

% Import some useful packages
\usepackage[margin=0.5in]{geometry} % narrow margins
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{amsmath}
\usepackage{xcolor}
\definecolor{LightGray}{gray}{0.95}

\title{Peer-review of assignment 5 for \textit{INF3331-dawoodah}}
\author{Reviewer 1, tobiasgm, {tobiasgm@student.matnat.uio.no} 
\\ Reviewer 2, sebastgj, {sebastgj@student.matnat.uio.no} 
\\ Reviewer 3, ferdinae, {ferdinae@ulrik.uio.no}}

\begin{document}
\maketitle

\section{Review \emph{}}\label{sec:review}

Reviewed with: Python version 3.5 (Homebrew) on MacBook Pro El Capitan

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{General feedback}
Overall a good solution with some problems as described below. Some general advice:
\begin{itemize}
  \item Would have been nice with a README with instructions on how to test the code.
  \item You could improve your docstrings by including information about prameter and return values (in a way that allows automatic generation of code documentation).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.1: Syntax highlighting}
\begin{itemize}
  \item Code is working as expected. Handles wrong cl-arguments well. Assumes well formatted syntax/ theme files.
  \item Well documented code, using docstrings. Remember to put all docstrings below the function/ class def they belong to.
  \item Well writtten, easily readable code broken up in functions in a sensible manner.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.2: Python syntax} \label{sec:assignment5.2}
\begin{itemize}	
  \item The regular expression seem to work as expected.	
  \item Two different color themes that work as expected.
  \item Possible improvements: You only match one possible way to write strings in python. Would have been nice with a regex that matched all variants of strings with single or double quotes. I think the regex would fail with some special cases like an escaped quote inside a string.
 \item The variable regex matches operators as well (for example (a == b).
 \item Would have been nice with coloring of some larger parts of relevant expressions, not only keywords like if, else class, but the whole construct.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.3: Syntax for your favorite language}
9 regex that cover different parts of the C language. As for 5.2, it would have been nice with some longer expressions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.4: Syntax for your second favorite language}
8 regex that cover different parts of the JAVA language. As for 5.2, it would have been nice with some longer expressions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.5: superdiff}
\begin{itemize}
  \item Some issues: Doesn`t handle several edge cases: Different lengths for input/ output files, removing a line and re-inserting the same line at some other place. Do a search for "longest common subsequence" problem for a possible solution.
    \item Missing some documentation/ comments on how the code is structured. Otherwise ok code apart from the issues mentioned.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Assignment 5.6:  Coloring diff}
Regex and theme implemented correctly.\\

- It would have been nicer if the output was colored automatically when mydiff.py is called. So that 5.5 and 5.6 is run more like one program.


\bibliographystyle{plain}
\bibliography{literature}

\end{document}